Pottery decor as networks on the Middle Niger

### 2024-03-08 analysis/paper/paper.Rmd

decor_20 <- decor_20 |>
  #isolated nodes are removed
  activate(nodes) |>
  filter(!node_is_isolated())

@@

```{r community detection, hide = 'results', echo=FALSE}
#sparsifying 
decor_graph_c <- decor_20 |>
  activate(nodes) |>
  mutate(louvain = as.character(group_louvain()))

>>>>

decor_20 <- decor_20 
  #isolated nodes are removed
  activate(nodes) |>
  filter(!node_is_isolated())

@@

```{r community detection, hide = 'results', echo=FALSE}

#sparsifying 
decor_graph_c <- decor_20 |>
  activate(nodes) |>
  mutate(louvain = as.character(group_louvain()))
